An Imaging Search for Post-MS Companions of Sirius B

### 2021-11-03 paper/paper.tex
remove unused references

There is limited knowledge of planetary systems around evolved stars. The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain. For a planet to survive the giant branch evolution, it first needs to escape engulfment as well as tidal shredding \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}. Surviving planets are subject to adiabatic orbit expansion \citep{jeansCosmogonicProblemsAssociated1924}, which can potentially de-stabilize multi-object systems, stellar winds, and high irradiation which enriches the circumstellar environment with metals and dust, and strongly heats planets close to the giant star \citep{verasPostmainsequencePlanetarySystem2016}. The expansion and tidal effects on the circumstellar environment create a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{5}{\au}.

@@

Sirius is one of the oldest studied star systems; the breadth and depth of knowledge about the binary gives exceptional precision for characterizing the circumstellar environment. Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}. \citet{vandenbosOrbitSiriusADS1960,gatewoodStudySirius1978} were the first to estimate dynamical masses using compilations of photographic plates from Lick and Yerkes observatories. \citet{bondSiriusSystemIts2017} used \textit{Hubble Space Telescope} (HST) data to compile the most precise orbital solution, to date, for Sirius. The dynamical masses were derived using this orbital solution and Hipparcos parallaxes: \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively. A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}. \citet{bondSiriusSystemIts2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.

@@

We also consider future space-based observations with the \textit{James Webb Space Telescope} (JWST), eliminating the effects of atmospheric seeing and the bright sky background. For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter. The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) are adequate for sub-AU observations of nearby WDs, depending on the contrast-limited performance of NIRCAM. Unfortunately, Sirius B is far too bright and too close to Sirius A to observe with JWST without severe saturation.

>>>>

There is limited knowledge of planetary systems around evolved stars. The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain. For a planet to survive the giant branch evolution, it first needs to escape engulfment as well as tidal shredding \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}. Surviving planets are subject to adiabatic orbit expansion \citep{jeansCosmogonicProblemsAssociated1924}, which can potentially de-stabilize multi-object systems, stellar winds, and high irradiation which enriches the circumstellar environment with metals and dust, and strongly heats planets close to the giant star \citep{mustillForetellingsRagnarokWorldengulfing2012,verasPostmainsequencePlanetarySystem2016}. The expansion and tidal effects on the circumstellar environment create a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{5}{\au}.

@@

Sirius is one of the oldest studied star systems; the breadth and depth of knowledge about the binary gives exceptional precision for characterizing the circumstellar environment. Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}. Most recently, \citet{bondSiriusSystemIts2017} used Hubble Space Telescope (HST) along with old photographic plates to compile the most precise orbital solution for Sirius, to date. They derived dynamical masses using their orbital solution and Hipparcos parallaxes: \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively. A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}. \citet{bondSiriusSystemIts2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.

@@

We also consider future space-based observations with the James Webb Space Telescope (JWST), eliminating the effects of atmospheric seeing and the bright sky background. For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter. The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) are adequate for sub-AU observations of nearby WDs, depending on the contrast-limited performance of NIRCAM. Unfortunately, Sirius B is far too bright and too close to Sirius A to observe with JWST without severe saturation.
